COVID-19 Policy-Compliance in Europe

### 2021-02-05 Analysis.Rmd
Renamed files

This analysis has shown that, interestingly, levels of compliance with mobility-reducing COVID-19-policies differ across selected European countries and that policy-compliance expresses an alarming, negative trend. Additionally, we were able to show how the *rate* at which policy-compliance decreases differs across European countries.

>>>>

This analysis has shown that, interestingly, levels of compliance with mobility-reducing COVID-19-policies differ across selected European countries and that policy-compliance expresses an alarming, negative trend, so that we can reject our Null-hypotheses. Additionally, we were able to show how the *rate* at which policy-compliance decreases differs across European countries.
